Towards Cloud Bursting for Extreme Scale Supercomputers\\ (Unrefereed Workshop Manuscript)

### 2014-07-01 paper/src/2_motivation.tex

\begin{table}[h]
\caption{\small TSUBAME thin node specification}
\label{tbl:spec}
\begin{center}
\begin{tabular}{|c|l|}
  \hline
  \cellcolor{lightgray} CPU      & Intel Xeon 2.93GHz CPU (4 cores)*2\\
  %(Hyperthreading enabled)\\
  \hline
  \cellcolor{lightgray} Memory   & 54GB (16 GB)    \\
  \hline
  \cellcolor{lightgray} SSD      & 120GB \\
  \hline
  \cellcolor{lightgray} GPU	 & NVIDIA Tesla K20X *3\\
  \hline
  \cellcolor{lightgray} Network  & QDR InfiniBnd *2 (80Gbps)\\
  \hline
\end{tabular}
\end{center}
\end{table}

\kento{Please explain what Public cloud is with example of Amazon EC2. Then, the details which is needed to mention for readers understand the rest of the sections.
  (1-1) Architecture (VM environment \& datacetners are geographically distributed)
  (1-2) Explain instance types which is related to this paper. Current draft does not mention any instance types.
  (1-3) introduce pay-as-you-go model to help readers understand the cost-based model in the modeling section 
  (1-4) [please add whatever you think it's needed]}

@@

There are many companies provide public cloud solution like google, IBM, Microsoft etc., among them, Amazon Elastic Compute Cloud (Amazon EC2)\cite{AMAZON_AWS} is one of the most famous public cloud, like other public cloud, Amazon EC2 privdes Virtualize computing, and owns computing and data centers in several geographic regions.

@@

In this study, we used general purpose m3.xlarge instance which has 4 vCPUs, 15GiB memory, 2*80GB SSD storage and high level Ethernet network condition in Tokyo region, we run Amazon Linux AMI 2014.03.2 (HVM), which is based on Linux 3.10 on these instances.

@@

\kento{Please explain (2-1) how we federate supercomputers with clouds. $=>$ Virtualize supercomputer (e.g. TSUBAME V) + VM on clouds. 
                      (2-2) what the advantages are. $=>$ VMs can provide the same execution environment on both supercomputers and clouds
                      (2-3) [please add whatever you think it's needed]}
When we try to federate supercomputer with public clouds, there are need to have a similiar performance and environment between these two systems.
So we virtualize the supercomputer(like TSUBAME V queue) and federate VMs running on supercomputers with VMs provided by public cloud.

@@

\kento{In this section, (3-1) First explain I/O problems in federation with clouds based on the cloud architecture explained in the above (1-1) as well as using Fig.1-4. 
                        (3-2) Then, please briefly clarfy why ``(A) I/O burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
                              (Remember we knew that I/O burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
                        (3-3) Another challenge is a choice of instance types for burst buffer, and understanding the trade-off between I/O perfomrance and the monetary cost. 
                              In addtion, the choice of instances, the trade-offs are changes depending on given a supercomputer and cloud environments, such as network throughput, PFS performance. 
                              That's why the ``(B) perfomrance modeling`` is important}
Although we virtualize supercomputer and obtain a similiar environment on both supercomputers and clouds, there are still several problems remains, for example, input data of applications running on supercomputer is usually stored in shared storages in the same system and can be read from and wrote to these storages with a extremely high throughput.

We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
Fig.~\ref{throughput TSUBAME} shows read and write throughput from TSUBAME V queue nodes (VM runing on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}) and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
However, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from Amazon.
We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, which is limited by Internet bandwidth, about 40-80 times smaller than throughput inside TSUBAME.
For data-sensitive application, low I/O throughput is devastating, especially for application running on supercomputers, furthermore, lower I/O throughput leads a longer execution time, according to Amazon pay-as-you-go policy, longer execution time means more cost.

However, when we look at Ethernet throughput inside Amazon as Fig.\ref{point to point connection AMAZON} shows, although we only show the result up to 8 pairs of nodes, each node achieved only 135MB/s (1GBit/s), the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
since when we running the benchmark, many other users were also running applications on Amazon, so we can assume that highest throughput 1GB/s (8Gbit/s) shown in Fig.~\ref{point to point connection AMAZON} is not the maximum bandwidth of Ethernet in Amazon EC2 .
Comparing Fig.~\ref{point to point connection AMAZON} with Fig.~\ref{throughput AMAZON to OURLAB} and Fig.~\ref{point to point connection LAB}, Ethernet throughput is much higher than Internet, it shows that our solution, by using I/O buffer nodes can achieve a higher Ethernet throughput than Internet.

To solve this problem, we propose our I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
Althought using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost, we will introduce a throughput-based model and a cost-based model to predict the throughput and overall cost.
%Moreover, the instance choice, number of I/O nodes depends on supercomputer and pulic cloud environment, in our following section, we will provide a performance modele

%when we try to move some jobs to public clouds after federation, the data 
\kento{Then, in the rest of the section, we explain (A) and (B)}

%\subsection{(Current Section 2)}
\kento{Please fit the below sentences to the above sections with additional explanations}

@@

%Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes \kento{Describe node specification in Table I}(VM runing on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}), which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
%On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, which has about 1GBit/s Internet access.
%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of interconnection inside supercomputer is quit larger than that from AMAZON.
%Also, if we compare the one nodes I/O throughput, 
%Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput \kento{??}
%If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.

>>>>

\begin{table}[h]
\caption{\small TSUBAME thin node specification}
\label{tbl:spec}
\begin{center}
\begin{tabular}{|c|l|}
  \hline
  \cellcolor{lightgray} CPU      & Intel Xeon 2.93GHz CPU (4 cores)*2\\
  %(Hyperthreading enabled)\\
  \hline
  \cellcolor{lightgray} Memory   & 54GB (16 GB)    \\
  \hline
  \cellcolor{lightgray} SSD      & 120GB \\
  \hline
  \cellcolor{lightgray} GPU	 & NVIDIA Tesla K20X *3\\
  \hline
  \cellcolor{lightgray} Network  & QDR InfiniBand *2 (80Gbps)\\
  \hline
\end{tabular}
\end{center}
\end{table}

%\kento{Please explain what Public cloud is with example of Amazon EC2. Then, the details which is needed to mention for readers understand the rest of the sections.
 % (1-1) Architecture (VM environment \& datacetners are geographically distributed)
  %(1-2) Explain instance types which is related to this paper. Current draft does not mention any instance types.
  %(1-3) introduce pay-as-you-go model to help readers understand the cost-based model in the modeling section 
  %(1-4) [please add whatever you think it's needed]}

@@

There are many companies provide public cloud solution like google, IBM, Microsoft etc., among them, Amazon Elastic Compute Cloud (Amazon EC2)\cite{AMAZON_AWS} is one of the most famous public cloud, like other public cloud, Amazon EC2 provides Virtualize computing, and owns computing and data centers in several geographic regions.

@@

In this study, we used general purpose m3.xlarge instance which has 4 vCPUs, 15GiB memory, 2*80GB SSD storage and high level interconnection network network condition in Tokyo region, we run Amazon Linux AMI 2014.03.2 (HVM), which is based on Linux 3.10 on these instances.

@@

%\kento{Please explain (2-1) how we federate supercomputers with clouds. $=>$ Virtualize supercomputer (e.g. TSUBAME V) + VM on clouds. 
%                      (2-2) what the advantages are. $=>$ VMs can provide the same execution environment on both supercomputers and clouds
%                      (2-3) [please add whatever you think it's needed]}
When we try to federate supercomputer with public clouds, there are need to have a similar performance and environment between these two systems.
So we virtualize the supercomputer(like TSUBAME U queue) and federate VMs running on supercomputers with VMs provided by public cloud.

@@

%\kento{In this section, (3-1) First explain I/O problems in federation with clouds based on the cloud architecture explained in the above (1-1) as well as using Fig.1-4. 
%                        (3-2) Then, please briefly clarfy why ``(A) I/O burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
%                              (Remember we knew that I/O burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
%                        (3-3) Another challenge is a choice of instance types for burst buffer, and understanding the trade-off between I/O perfomrance and the monetary cost. 
%                              In addtion, the choice of instances, the trade-offs are changes depending on given a supercomputer and cloud environments, such as network throughput, PFS performance. 
%                              That's why the ``(B) perfomrance modeling`` is important}
Although we virtualize supercomputer and obtain a similar environment on both supercomputers and clouds, there are still several problems remains, for example, input data of applications running on supercomputer is usually stored in shared storages in the same system and can be read from and wrote to these storages with a extremely high throughput.

We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
Fig.~\ref{throughput TSUBAME} shows read and write throughput from TSUBAME V queue nodes (VM running on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}) and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
However, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from Amazon.
We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, which is limited by Internet bandwidth, about 40-80 times smaller than throughput inside TSUBAME.
For data-sensitive application, low I/O throughput is devastating, especially for application running on supercomputers, furthermore, lower I/O throughput leads a longer execution time, according to Amazon pay-as-you-go policy, longer execution time means more cost.

However, when we look at interconnection network throughput inside Amazon as Fig.\ref{point to point connection AMAZON} shows, although we only show the result up to 8 pairs of nodes, each node achieved only 135MB/s (1GBit/s), the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
since when we running the benchmark, many other users were also running applications on Amazon, so we can assume that highest throughput 1GB/s (8Gbit/s) shown in Fig.~\ref{point to point connection AMAZON} is not the maximum bandwidth of interconnection network in Amazon EC2 .
Comparing Fig.~\ref{point to point connection AMAZON} with Fig.~\ref{throughput AMAZON to OURLAB} and Fig.~\ref{point to point connection LAB}, interconnection network throughput is much higher than Internet, it shows that our solution, by using I/O buffer nodes can achieve a higher interconnection network throughput than Internet.

To solve this problem, we propose our I/O burst buffer architecture, since usually Internet throughput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transferring file between two systems, hence achieve a high I/O throughput.
Although using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost, we introduce a throughput-based model and a cost-based model to predict the throughput and overall cost.
%Moreover, the instance choice, number of I/O nodes depends on supercomputer and pulic cloud environment, in our following section, we will provide a performance modele

%when we try to move some jobs to public clouds after federation, the data 
%\kento{Then, in the rest of the section, we explain (A) and (B)}

%\subsection{(Current Section 2)}
%\kento{Please fit the below sentences to the above sections with additional explanations}

@@

%Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes \kento{Describe node specification in Table I}(VM running on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}), which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
%On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, which has about 1GBit/s Internet access.
%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of interconnection inside supercomputer is quit larger than that from AMAZON.
%Also, if we compare the one nodes I/O throughput, 
%Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput \kento{??}
%If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.

### 2014-07-01 paper/src/3_burst_buffer.tex

\section{I/O Bursting Buffer Overview}
% Why I/O server in client nodes
\label{sec:burst_buffer}

@@

An overview of I/O burst buffer architecture and two kinds of buffer model: one-side buffer and two-side buffer are described in this section.
As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, for write I/O data, if buffer queue in I/O buffer nodes is not full, data can first be buffered in buffer queue in the same system, and then be transferred to final storage system, and for reading, if that file is stored in the buffer queue, computing nodes can read from I/O nodes through Ethernet.
In other cases (buffer queue is full when issue a write requst or requsted file is not stored in buffer queue when issue a read request we call it cache miss), an read from or write back operation described below will be executed. 
\kento{how about read ?}.
%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.

@@

%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application and I/O burst buffer nodes.
Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.

Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data, communicate with I/O buffer nodes, including send I/O requset and send or receive I/O data.

When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O server will try to transfer I/O data to buffer queue in I/O burst buffer, if buffer queue in not full, I/O data will be sent to I/O burst buffer via Ethernet and can be seen among computing nodes in the same system after that.
However if buffer queue is full, I/O server will block user application and wait until buffer queue is ready to recieve new I/O data, causing a low I/O throughput.

@@

Similiarly when user issue a read request, there are two conditions: required file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.

@@

In this section we describe read and write operations when cache miss happens.%file is not in I/O buffer nodes or file needs to be write back to storage in another system.
We propose two kinds of model: one-side buffer and two-side buffer.

@@

%the bottleneck is still Internet throughput, since interconnection is far faster than Internet.
However since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than tranferring time, and compress data can make more data buffered in buffer queue.
Also, unlike one-side buffer, two-side buffer do not require storage to be opened to Internet, only required several I/O nodes have access to Internet.

For these reasons, in the following section, we will use two-side buffer model as our read from and write back model in I/O burst buffer.
%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.

>>>>

\section{I/O Burst Buffer Overview}
% Why I/O server in client nodes
\label{sec:burst_buffer}

@@

An overview of I/O burst buffer architecture and two kinds of buffer model: one-side buffer and two-side buffer are described in this section.
As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, for write I/O data, if buffer queue in I/O buffer nodes is not full, data can first be buffered in buffer queue in the same system, and then be transferred to final storage system, and for reading, if that file is stored in the buffer queue, computing nodes can read from I/O nodes through interconnection network.
In other cases (buffer queue is full when issue a write request or requested file is not stored in buffer queue when issue a read request we call it cache miss), an read from or write back operation described below will be executed. 
%\kento{how about read ?}.
%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.

@@

%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst nodes}, computing nodes run user's application and I/O burst nodes.
Among I/O burst nodes, there is a master nodes, which maintain a global buffer queue and a namespace, control buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.

Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst nodes.
In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data, communicate with I/O buffer nodes, including send I/O request and send or receive I/O data.

When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O server will try to transfer I/O data to buffer queue in I/O burst buffer, if buffer queue in not full, I/O data will be sent to I/O burst buffer via interconnection network and can be seen among computing nodes in the same system after that.
However if buffer queue is full, I/O server will block user application and wait until buffer queue is ready to receieve new I/O data, causing a low I/O throughput.

@@

Similarly when user issue a read request, there are two conditions: required file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.

@@

In this section we describe read and write operations when cache miss happens.
%file is not in I/O buffer nodes or file needs to be write back to storage in another system.
We propose two kinds of model: one-side buffer and two-side buffer.

@@

%the bottleneck is still Internet throughput, since interconnection is far faster than Internet.
However since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than transferring time, and compress data can make more data buffered in buffer queue.
Also, unlike one-side buffer, two-side buffer do not require storage to be opened to Internet, only required several I/O nodes have access to Internet.

For these reasons, in the following section, we use two-side buffer model as our read from and write back model in I/O burst buffer.
%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
